%-------------------------
% Resume in LateX
% Author : Prakhar Srivastava
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & #2                 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & #2                 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{https://www.linkedin.com/in/prakhar-srivastava-b14lko}{\Large Prakhar Srivastava}} & Email: \href{mailto:prasri510@gmail.com}{prasri510@gmail.com}\\
\href{https://www.linkedin.com/in/prakhar-srivastava-b14lko}{LinkedIn: linkedin.com/in/prakhar-srivastava-b14lko \faExternalLink} & Mobile: \href{tel:+919873851094}{+919873851094} \\
Bangalore, Karnataka, India & \href{https://github.com/PraSri} {GitHub: github.com/PraSri \faExternalLink}\\

\end{tabular*}

%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
\small{
    Senior Software Engineer with 8 years of experience building scalable microservices (Java, Scala, Python) and real‑time data management systems (Kafka, MySQL, ES).
    Expertise in cloud‑native architectures (AWS/GCP/Azure) and event‑driven patterns, with hands‑on experience in Agentic AI.
}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart


\resumeSubheading
{Walmart Global Tech India}{Bengaluru, Karnataka, India}
{Senior Software Engineer}{Aug 2022 - Present}
\resumeItemListStart
\resumeItem{AdTech Catalog Services}
{Architected and deployed 5+ \textbf{Scala}-based microservices using the \textbf{Play} framework and \textbf{ElasticSearch} for AdTech catalog data management. Processed 1M+ daily search requests over 100M+ products, reducing latency by 30\% and enabling 100K+ advertisers to run campaigns.}
\resumeItem{AdTech MCP server}
{Designed and implemented the AdTech Catalog MCP Server using \textbf{Spring AI}, enabling seamless advertiser onboarding and campaign activation through Walmart’s AI Agent platform, Marty.}
\resumeItem{Display Ads Inventory Management}
{Developed \textbf{Java/Spring Boot} forecasting APIs powered by \textbf{Vespa} to manage ad inventory for 10K+ advertisers. Achieved 99.9\% uptime and increased ad revenue by 25\% for display ads.}
\resumeItemListEnd
\resumeSubheading
{Paytm}{Noida, India}
{Senior Software Engineer}{May 2021 - Aug 2022}
\resumeItemListStart
\resumeItem{Recommendation Service}
{Architected a \textbf{Spring Boot} microservice employing \textbf{Elasticsearch} enabling 50M+ users to search and locate nearby stores on the Home page.}
\resumeItem{Loyalty Points and Wallet Service}
{Built scalable \textbf{Java/Kotlin} microservices using \textbf{Kafka} and \textbf{DynamoDB} for the Loyalty Points System. Handles 10M+ monthly transactions for 50M+ users with 99.9\% uptime.}
\resumeItem{Merchant Onboarding}
{Developed \textbf{Kotlin} based services and schedulers for back office ops to manage 100K+ merchants with 10K+ new merchants monthly and reduced onboarding time by 60\%.}
\resumeItemListEnd

\resumeSubheading
{Clearwater Analytics}{Noida, India}
{Software Development Engineer}{Feb 2020 - May 2021}
\resumeItemListStart
\resumeItem{Portfolio Management \& Data Reconciliation}
{Enhanced \textbf{Java} based legacy system and built internal ETLs for financial data reconciliation for 100+ clients globally, improving data processing speed by 45\%.}
\resumeItemListEnd

\resumeSubheading
{Qualitest}{Noida, India}
{Software Engineer}{Jun 2018 - Feb 2020}
\resumeItemListStart
\resumeItem{US based News Website}
{Improved system reliability by building Java-based automation test suite using JUnit, reducing regression testing time by 50\%, achieving 95\% test coverage, and increasing deployment frequency from monthly to weekly.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem
{\textbf{Languages}}{Java, Scala, Kotlin, C++, Python, SQL}
\resumeSubItem
{\textbf{Frameworks}}{Spring Boot, Kafka, Play, Akka, Apache Spark, Swagger, JUnit}
\resumeSubItem
{\textbf{AI}}{Spring AI, Google ADK, GCP Vertex AI, Ollama, LangGraph, LangChain, Copilot, Cursor, MCP, RAG}
\resumeSubItem
{\textbf{Databases}}{MySQL, DynamoDB, Elasticsearch, Solr, Apache Hive, Presto, Vespa}
\resumeSubItem
{\textbf{Tools/Cloud}}{GCP, AWS, Docker, Kubernetes, Git, Jenkins, Airflow, Redis, JMeter, Maven, Gradle, Postman}
\resumeSubHeadingListEnd

%-----------PROJECTS & CERTIFICATIONS-----------------
\section{Personal Projects \& Certifications}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://www.kaggle.com/learn-guide/5-day-agents}{AI Agents Intensive Course with Google \faExternalLink}}
{A hands-on program, crafted by Google’s ML researchers and engineers to help developers explore the foundations and practical applications of AI agents.
Its core components include models, tools, orchestration, memory and evaluation.
Mastered the end-to-end architecture of production-ready AI agents, including model selection, tool integration, memory systems, orchestration, and evaluation frameworks.}
\resumeSubItem{\href{https://kaggle.com/competitions/agents-intensive-capstone-project/writeups/agent-fintrac}{AI financial advisor - Kaggle Hackathon Project \faExternalLink}}
{Developed a proactive AI financial advisor using \textbf{Google ADK}
that prevents impulsive spending by providing real-time alternatives and personalized recovery plans.}
\resumeSubItem{\href{https://coursera.org/share/54bf8156523e1681b3689fb9dc70395e}{Certification in Develop Generative AI Applications with IBM \faExternalLink}}
{Learned GenAI fundamentals and LangChain’s modular tools to design context-aware AI applications using prompts, chains, and agents.
Built and evaluated a Flask-based GenAI app with structured outputs and optimized model selection for reliable performance.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{JSS ACADEMY OF TECHNICAL EDUCATION, NOIDA}{Noida, India}
{B.Tech CSE; GPA: 8.2/10}{Aug. 2014 -- July. 2018}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}







